---
output:
  md_document: 
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

Swedish historical administrative maps
======================================

A R data package of Swedish historical administrative boundaries for parishes and counties 1634-1990.

**Data files are not incuded**

## County map

```{r county_ex, message = FALSE}
library(histmaps)
library(sp)
map <- hist_boundaries(1800, "county")
plot(map)
```

## Parish map

```{r parish_ex, message = FALSE}
library(knitr)
library(ggplot2)
library(dplyr)

p_map <- hist_boundaries("1866-06-06", "parish", "df")

st_map <- p_map %>% filter(county < 3)
ggplot(st_map, aes(long, lat, group = group)) +
  geom_polygon(fill = "lightgrey", color = "black") + coord_equal() + 
  theme_minimal()
```

## Period map

As parishes changes boundaries over the course of history a given map a certain year is not representative of the boundaries another year. To create a map for a period the parishes need to be aggregated to the lowest common denominator for that period. You can do this by supplying a date range to `hist_boundaries`.

```{r period_dat}
period_map <- hist_boundaries(c(1900, 1920)) 
```

The function returns a list where the first object is the map data and the second is a lookup table for aggregating your data to the new artificial parish boundaries. 

```{r period_plot}
plot(period_map$map)
```


```{r period_lookup}
kable(head(period_map$lookup))
```
